Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-16 article_review/reviewer_letter.tex
Adding changes on manuscript
changes manuscript

\textbf{Minor comments}:
\begin{itemize}
\item[a.] page 1, column 1, lines 23-24: "through" instead of "trough"
\item[b.] page 2, column 2, equation (7): why use a biased estimator for $\sigma^2$ ?
\item[c.] page 4, column 2, equation (14): it is not clear how $\ell$ is chosen on the RHS, and whether or not the inequality holds for all $\ell \leq m$ or for some specific value of $\ell$ ? Please clarify.
\item[d.] page 4, column 2, line 42: is it not instead "...the error bound $\epsilon_{\hat{I}}$" (hat on subscript I?)?
\item[e.] page 5, column 2 line 55: not clear what you mean by "independent" in "two independent Sobol' sequences", especially if the designs are not randomized. From [4] it looks like you are using a 2d-dimensional Sobol' sequence and assign the first d coordinates to the first design and the next d ones to the second design. Please explain this more and state what properties you need for these sequences.
\item[f.] page 6, column 2, line 32: is the "iid" property valid across the indices i, i.e., the n vectors have to be independent? If so, this would invalidate the use of a Sobol' sequence to create these vectors, so please clarify this point.
\item[g.] page 9, column 2 , "real case model". There are some imprecisions in this part: lines 15-16, it should be the "discounted payoff" and not just "payoff", rho is the risk-free interest rate (not just interest rate). More importantly, the authors directly give the discounted payoff in terms of the Brownian motion without stating what model is used for the stock price and without stating that for the purpose of pricing one should work under the risk-neutral measure. Please clarify this so that the financial motivation for this problem is properly done.
\end{itemize}

@@

{\color {blue} We acknowledge that Sobol' indices are theoretically invariant by adding a constant shift $c$ to the studied function. As underlined by the reviewer, the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the errors bounds for the others integrands ($\vI_1$, $\vI_2$ and $\vI_4$). More generally, our algorithm depends on the analytical expression of the Sobol' index estimator considered.

@@

@@

{\color{blue} The Sobol' g-function has been modified according to the reviewer remark. Corresponding tables and figures have changed.}

@@

{\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database. Section $5.2$ has been reworked to introduce this new test function. Our results are compared to formers obtained by screening approaches.}

>>>>

\textbf{Minor comments}:
\begin{itemize}
\item[a.] page 1, column 1, lines 23-24: "through" instead of "trough"

{\color{blue} The typo has been corrected.}
\item[b.] page 2, column 2, equation (7): why use a biased estimator for $\sigma^2$ ?

{\color{blue} The biased estimator has been replaced by the unbiased one.}
\item[c.] page 4, column 2, equation (14): it is not clear how $\ell$ is chosen on the RHS, and whether or not the inequality holds for all $\ell \leq m$ or for some specific value of $\ell$ ? Please clarify.
\item[d.] page 4, column 2, line 42: is it not instead "...the error bound $\epsilon_{\hat{I}}$" (hat on subscript I?)?

{\color{blue} The typo has been corrected.}
\item[e.] page 5, column 2 line 55: not clear what you mean by "independent" in "two independent Sobol' sequences", especially if the designs are not randomized. From [4] it looks like you are using a 2d-dimensional Sobol' sequence and assign the first d coordinates to the first design and the next d ones to the second design. Please explain this more and state what properties you need for these sequences.

{\color{blue} The paragraph has been reworked. The reviewer guessed right. We use a 2d-dimensional Sobol' sequence and assign its first d dimensions to the first design and the remaining ones to the second design. Then, each Sobol' sequence is scrambled independently; except in Variant B where the scrambling is the same to insure that the two designs are replicated designs of order one.

As for the properties of the Sobol' sequences, the ones used in this paper are generated with the directional numbers found by S. Joe and F. Y. Kuo (2008). These directional numbers insure better two-dimensional projections of the resulting Sobol' sequences.}

\item[f.] page 6, column 2, line 32: is the "iid" property valid across the indices i, i.e., the n vectors have to be independent? If so, this would invalidate the use of a Sobol' sequence to create these vectors, so please clarify this point.
\item[g.] page 9, column 2 , "real case model". There are some imprecisions in this part: lines 15-16, it should be the "discounted payoff" and not just "payoff", rho is the risk-free interest rate (not just interest rate). More importantly, the authors directly give the discounted payoff in terms of the Brownian motion without stating what model is used for the stock price and without stating that for the purpose of pricing one should work under the risk-neutral measure. Please clarify this so that the financial motivation for this problem is properly done.

{\color{blue} The ``real case model'' has been replaced with a new one as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections.} 
\end{itemize}

@@

{\color {blue} We acknowledge that analytical formulas of Sobol' indices are invariant by adding a constant shift $c$ to the function $f$. As underlined by the reviewer, in our algorithm the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the errors bounds for the others integrands ($\vI_1$, $\vI_2$ and $\vI_4$). More generally, our algorithm depends on the analytical expression of the Sobol' index estimator considered.

@@

{\color{blue} We agree with the reviewer that the effective dimension of the higher dimensions integrand might be lower than its lower dimensions counterpart. However, evaluating the effective dimension of each integrands already requires a large number of model evaluations itself (\textit{c.f.} Wang. X and Fang. K.-T., 2003).

Since evaluating the effective dimension is not in the scope of this paper, we propose the following. The original statement has been replaced with the assumption that the higher dimensions integrand possesses a higher effective dimension. Then, this assumption is tested on each example by plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats. The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}

@@

{\color{blue} The Sobol' g-function has been modified according to the reviewer remark. There were no drastic changes observed. As a matter of fact, the failure rates have improved for all three approaches (Variant A.a, A.b and B).}

@@

{\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database. Section $5.2$ has been reworked to introduce this new test function. Our results are compared to formers obtained by screening approaches (Moon, H. (2010)).}
